\documentclass[12pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[greek,english]{babel}
\usepackage{xgreek}

% FONTS
% \usepackage{xunicode}
\usepackage{xltxtra}
% \defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode
% \setromanfont [Ligatures={Common}, BoldFont={GFS Artemisia Bold}, ItalicFont={Gentium Italic}]{Gentium}
% \setmonofont[Scale=0.8]{GFS Artemisia} 
\setmainfont{GFS Artemisia}

\usepackage{geometry} 
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{8mm}
\setlength\parskip{5mm}

% \usepackage{unicode-math}
\usepackage[shortlabels]{enumitem}

% diagram support
\usepackage{tikz}
\usetikzlibrary{arrows,calc,patterns,positioning,shapes}
\usetikzlibrary{decorations.pathmorphing}

\tikzset{
modal/.style={>=stealth',shorten >=1pt,shorten <=1pt,auto,
    node distance=1.5cm,thick},
world/.style={circle,draw,minimum size=1cm,fill=gray!15},
point/.style={circle,draw,fill=black,inner sep=0.5mm},
reflexive/.style={->,in=120,out=60,loop,looseness=#1},
reflexive/.default={5},
reflexive point/.style={->,in=135,out=45,loop,looseness=#1},
reflexive point/.default={25},
}
\tikzset{
reflexive above/.style={->,loop,in=120,out=60,looseness=#1},
reflexive above/.default={7},
reflexive below/.style={->,loop,in=240,out=300,looseness=#1},
reflexive below/.default={7},
reflexive left/.style={->,loop,in=150,out=210,looseness=#1},
reflexive left/.default={7},
reflexive right/.style={->,loop,in=30,out=330,looseness=#1},
reflexive right/.default={7}
}

\title{Άσκηση 1.3 από \\``Reasoning About Knowledge (1995)''}
\author{Καμινάρης Κωνσταντίνος}
\date{11/3/2024}

%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%

\begin{document}

\setlanguage{greek} %% this is to activate greek hyphenation

\maketitle

\section*{Άσκηση 1.3}
\subsection*{Ερώτηση}
The wise men puzzle is a well-known variant of the muddy children puzzle.
The standard version of the story goes as follows: There are three wise men. It is
common knowledge that there are three red hats and two white hats. The king puts
a hat on the head of each of the three wise men, and asks them (sequentially) if they
know the color of the hat on their head. The first wise man says that he does not
know; the second wise man says that he does not know; then the third wise man says
that he knows.

\begin{enumerate}[label=\emph{\alph*}]
    \item What color is the third wise man’s hat?
    \item We have implicitly assumed in the story that the wise men can all see. Suppose we assume instead that the third wise man is blind and that it is common knowledge that the first two wise men can see. Can the third wise man still figure out the color of his hat?
\end{enumerate}

\newpage

\subsection*{Απάντηση για ταυτόχρονες αποκρίσεις}

\input{simultaneous_answers.tex}

\subsection*{Απάντηση για διαδοχικές αποκρίσεις}

\input{sequential_answers.tex}

\subsection*{Συμπέρασμα}

\input{result.tex}

\end{document}
